Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-20 SDSS-2023/testing-charts-accuracy.qmd
with current pdf

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
short-title: Testing charts in surveys # running title
author:
  - first: Kiegan                 # first name
    first-init: K.              # initial of first name
    last: Rice                  # last name
    marker: 1               # identifier for the affiliation
    footnote-id: 1              # optional identifier for the footnote
    email: foo@bar.com          # optional email address
  - first: Heike
    first-init: H.
    last: Hofmann
    marker: 2
  - first: Nola
    first-init: N.
    last: duToit
    marker: 1
  - first: Edward
    first-init: E.
    last: Mulrow
    marker: 1
footnote:
  - content: Corresponding author
    type: corresp               # set type for the corresponding author
    id: 1
affiliation:
  - institution: NORC at the University of Chicago
    country: United States
    marker: 1
  - institution: Iowa State University
    department: Statistics
    country: United States
    marker: 2
bibliography: references.bib
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
  \usepackage{booktabs}
  \usepackage{graphicx}
  \usepackage{hyperref}
documentclass: jds
format:
  pdf: 
    include-in-header: authors.tex
    keep-tex: true
  html: default
editor: 
  markdown: 
    wrap: sentence
---

@@

```{r}
#| label: fig-tasks
#| fig-cap: "Each of the visual stimuli presented to viewers. In each bar chart, two pieces are marked. The larger piece in each chart is piece A or C. "
#| fig-subcap:
#| - "**Vertical stacked bar, unaligned**"
#| - "**Horizontal stacked bar, unaligned**"
#| - "**Wide horizontal stacked bar, unaligned**"
#| - "**Vertical stacked bar, aligned**"
#| - "**Horizontal stacked bar, aligned**"
#| - "**Wide horizontal stacked bar, aligned**"
#| layout-nrow: 2
#| out-width: 100%
knitr::include_graphics("images/vertical-ab.PNG")
knitr::include_graphics("images/round3/horizontal-ab.PNG")
knitr::include_graphics("images/round3/hwide-ab.PNG")
knitr::include_graphics("images/vertical-cd.PNG")
knitr::include_graphics("images/round3/horizontal-cd.PNG")
knitr::include_graphics("images/round3/hwide-cd.PNG")
```

>>>>

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
short-title: Testing charts in surveys # running title
author:
  - first: Kiegan                 # first name
    first-init: K.              # initial of first name
    last: Rice                  # last name
    marker: 1               # identifier for the affiliation
    footnote-id: 1              # optional identifier for the footnote
    email: foo@bar.com          # optional email address
  - first: Heike
    first-init: H.
    last: Hofmann
    marker: 2
  - first: Nola
    first-init: N.
    last: duToit
    marker: 1
  - first: Edward
    first-init: E.
    last: Mulrow
    marker: 1
footnote:
  - content: Corresponding author
    type: corresp               # set type for the corresponding author
    id: 1
affiliation:
  - institution: NORC at the University of Chicago
    country: United States
    marker: 1
  - institution: Iowa State University
    department: Statistics
    country: United States
    marker: 2
bibliography: references.bib
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
  \usepackage{booktabs}
  \usepackage{graphicx}
  \usepackage{hyperref}
documentclass: jds
format:
  html: default
  pdf: 
    include-in-header: authors.tex
    keep-tex: true
editor: 
  markdown: 
    wrap: sentence
---

@@

```{r}
#| label: fig-tasks
#| fig-cap: "Each of the visual stimuli presented to viewers. In each bar chart, two pieces are marked. The larger piece in each chart are pieces B and D. "
#| fig-subcap:
#| - "Vertical stacked bar, unaligned"
#| - "Horizontal stacked bar, unaligned"
#| - "Wide horizontal stacked bar, unaligned"
#| - "Vertical stacked bar, aligned"
#| - "Horizontal stacked bar, aligned"
#| - "Wide horizontal stacked bar, aligned"
#| layout-nrow: 2
#| out-width: 100%
knitr::include_graphics("images/vertical-ab.PNG")
knitr::include_graphics("images/round3/horizontal-ab.PNG")
knitr::include_graphics("images/round3/hwide-ab.PNG")
knitr::include_graphics("images/vertical-cd.PNG")
knitr::include_graphics("images/round3/horizontal-cd.PNG")
knitr::include_graphics("images/round3/hwide-cd.PNG")
```
